Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-09 ICML-submission/related-work.tex

\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
boosting under bandit feedback, where one can view online boosting as online
linear classification by treating each base hypothesis as a separate feature.
\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that
the set of examples is strongly separable by a convex combination of base hypotheses
with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
mistake bound. \cite{Zhang-Jung-Tewari-2018} considers an online weak learning
condition, which implies that all examples is separable by a convex combination of base hypotheses with a margin (See~\cite{Mukherjee-Schapire-2013}, Theorem 3).
Under this condition, it gives
a boosting algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
mistake bound.

There has been much literature on the contextual bandit learning problem~\citep{Auer-2003, Langford-Zhang-2007}.
In this problem, the learner is given a policy class $\Pi$, and
at each timestep $t$, an example $x_t$ is shown, with an associated cost vector $c_t$ hidden.
The learner then takes an action $\hat{y}_t$, and observed the incurred cost $c_t$.
The goal of the learner is to minimize its regret $\sum_{t=1}^T c_t(\hat{y}_t) - \min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
The online bandit multiclass learning problem is a special case of the contextual bandits problem,
where the cost $c_t(i)$ is the classification error $I(i \neq y_t)$,
and the policy class $\Pi$ is the set of linear classifiers
$\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times d}}$.
A series of works in the contextual bandits learning literature focus on
oracle-efficiency~\citep{DudikHKKLRZ11, Monster:2014, RakhlinS16, Syrgkanis2016a, Syrgkanis2016b}.
Specifically, they assume access to a policy optimization
oracle that receives a set of cost-sensitive learning examples and policy class $\Pi$,
return the policy in $\Pi$ that minimizes its empirical cost on the examples, and the algorithm
only call the oracle a polynomial number of times.
However, these algorithms are not truly computationally efficient in our setting,
as it is NP-hard in general to find a linear classifier that minimizes the empirical cost over a set of examples~\citep{arora1997hardness}.

%as algorithms generate cost-sensitive examples that may not be linearly separable
%Algorithms that satisfy oracle efficiency has been proposed in the literature, for
%example.

Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory of contextual bandits
with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
\sum_{t=1}^T \frac{1}{K} \sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$,
where $\calF$ contains score functions $f$
such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
\gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic mistake upper bounds under various settings of $\calF$,
including parametric and nonparametric classes. On the other hand, it gives
an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
application of this result to the online bandit multiclass learning problem
yields an algorithm with a $O(\sqrt{T})$ mistake bound in the strong
linearly separable setting.

>>>>

\cite{Chen-Lin-Lu-2014, Zhang-Jung-Tewari-2018} study online bandit multiclass
boosting under bandit feedback, where one can view online boosting as online
linear classification by treating each base hypothesis as a separate feature.
\cite{Chen-Lin-Lu-2014}'s online weak learning condition implies that there is a
convex combination of base hypotheses that one-versus-all separates all examples
with a margin. Under this condition, it gives an algorithm with a $O(T^{3/4})$
mistake bound. \cite{Zhang-Jung-Tewari-2018} considers an online weak learning
condition that implies that there is a convex combination of base hypotheses
that weakly separates all examples with a margin
(See~\cite{Mukherjee-Schapire-2013}, Theorem 3). Under this condition, it gives
an algorithm with a $O(\sqrt{T})$ mistake bound with the knowledge of the edge
parameter. In addition, it gives an adaptive algorithm with a $O(T^{3/4})$
mistake bound.

The online bandit multiclass learning is a special case of the contextual bandits
problem~\cite{Auer-2003, Langford-Zhang-2008}, where the cost is the classification error.
A series of works in the contextual bandits learning literature focuses on
oracle-efficiency, that is, they assume access to an
oracle that given a set of cost-sensitve learning examples,

Recently, \cite{Foster-Krishnamurthy-2018} developed a rich theory on contextual bandits
with surrogate losses, focusing on benchmarks of the form $\min_{f \in \calF}
\frac{1}{K} \sum_{i=1}^K l_t(i) \phi( f_i(x) )$, where $\calF$ contains function $f$
such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac s
\gamma, 0)$ and $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic mistake upper bounds under various settings of $\calF$,
for instance parametric and nonparametric classes. On the other hand, it gives
an efficient algorithm that has a $O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$.

### 2019-01-09 ICML-submission/title-and-abstract.tex

\documentclass[12pt]{article}

% LaTeX packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[singlelinecheck=false]{caption}
\usepackage{fullpage}
\usepackage[colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{thmtools}
\usepackage{tikz}
\usepackage{color}
\usepackage{comment}
\usepackage{commath}
\usepackage{dsfont}

% TikZ packages
\usetikzlibrary{arrows}
\usetikzlibrary{angles}
\usetikzlibrary{backgrounds}
\usetikzlibrary{calc}
\usetikzlibrary{cd}  % commutative diagrams
\usetikzlibrary{intersections}
\usetikzlibrary{patterns}
\usetikzlibrary{shapes}
\usetikzlibrary{through}

% Math environments
\newtheorem{definition}{Definition}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}

% Math symbols and commands
\newcommand{\calF}{\mathcal{F}}
\newcommand{\one}{\mathds{1}}
\newcommand{\R}{\mathbb{R}}  % set of real numbers
\newcommand{\indicator}[1]{\mathbf{1}\left[#1 \right]} % indicator
\newcommand{\ip}[2]{\left\langle #1, #2 \right\rangle} % inner product
%\newcommand{\norm}[1]{\left\| #1 \right\|}  % norm of a vector or a matrix
%\DeclareMathOperator*{\deg}{deg}

\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\Exp}{\mathbf{E}}  % expected value
\DeclareMathOperator{\diff}{d \!} % differential
\DeclareMathOperator*{\polylog}{polylog}

\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkred}{rgb}{0.7,0,0}
\definecolor{teal}{rgb}{0.3,0.8,0.8}
\definecolor{orange}{rgb}{1.0,0.5,0.0}
\definecolor{purple}{rgb}{0.8,0.0,0.8}
\definecolor{blue}{rgb}{0.0,0.0,1.0}
\newcommand{\kibitz}[2]{{\textcolor{#1}{\textsf{\footnotesize #2}}}}
\newcommand{\alina}[1]{\kibitz{darkred}{[AB: #1]}}
\newcommand{\david}[1]{\kibitz{darkgreen}{[DP: #1]}}
\newcommand{\balazs}[1]{\kibitz{purple}{[BS: #1]}}
\newcommand{\deva}[1]{\kibitz{teal}{[DT: #1]}}
\newcommand{\chenyu}[1]{\kibitz{orange}{[CW: #1]}}
\newcommand{\chicheng}[1]{\kibitz{blue}{[CZ: #1]}}

\title{Online Multiclass Linear Classification with Bandit Feedback}

\author{
Alina Beygelzimer \and
D\'avid P\'al \and
Bal\'azs Sz\"or\'enyi \and
Devanathan Thiruvenkatachari \and
Chen-Yu Wei \and
Chicheng Zhang
}

\begin{document}

\maketitle

@@

\input{introduction}
\input{related-work}
\input{notions-of-linear-separability}
\input{algorithm-for-strongly-linearly-separable-data}
\input{from-linear-separability-to-strong-linear-separability}
\input{proofs-of-polynomial-approximation-theorems}
\input{nearest-neighbor-algorithm}
\input{np-hardness-of-the-weak-labeling-problem}
\input{mistake-lower-bound-for-ignorant-algorithms}

\bibliographystyle{plainnat}
\bibliography{biblio}

\appendix

\input{appendix-multiclass-perceptron}

\end{document}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Online Multiclass Linear Classification with Bandit Feedback}

\twocolumn[
\icmltitle{Online Multiclass Linear Classification with Bandit Feedback}

\begin{icmlauthorlist}
\icmlauthor{Alina Beygelzimer}{yahoo}
\icmlauthor{D\'avid P\'al}{yahoo}
\icmlauthor{Bal\'azs Sz\"or\'enyi}{yahoo}
\icmlauthor{Devanathan Thiruvenkatachari}{nyu}
\icmlauthor{Chen-Yu Wei}{usc}
\icmlauthor{Chicheng Zhang}{microsoft}

\end{icmlauthorlist}

\icmlaffiliation{yahoo}{Yahoo Research, New York, NY, USA}
\icmlaffiliation{nyu}{New York University, New York, MA, USA}
\icmlaffiliation{usc}{University of Southern California, Los Angeles, CA, USA}
\icmlaffiliation{microsoft}{Microsoft Research, New York, NY, USA}

\icmlcorrespondingauthor{D\'avid P\'al}{davidko.pal@gmail.com}

\icmlkeywords{multi-armed bandits, contextual bandits, online classification, linear separability}

\vskip 0.3in
]

\printAffiliationsAndNotice{}

@@
